Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
more updates

Our approach was capable of slicing a total of $260$ faults from $5$ different 
subjects. We are still running experiments for the \closure{} and \cmath{} projects.
(The results of these faults will be integrated on the camera-ready if accepted).
$33$ of the $260$ faults do not include the faulty statements in the slicer report
after slicing.

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
presents the number of faults where at least one of the faulty statements appears 
in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
classes of the projects. \combpar{k} finds the faulty statements faster than 
\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, an improvement
of $5.2\%$.

@@

%For both \comb{}-5 and \comb{}-10, diagnosability increases 55.56\%. However, top-5 has less classes to minimize than top-10.

Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant. Shapiro-Wilk ~\cite{10.2307/2333709} tests the null hypothesis that results are drawn from a normal distribution. The test is perfomed for the three techniques under evaluation (\sfl{}, \comb{}-5, \comb{}-10). With 99 \% of confidence, the results tell us that the distributions are not normal. Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman ~\cite{10.2307/2279372}. The null-hypothesis is that all distributions are the same. With 99 \% of confidence, the results show that the distributions are not all the same. In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis \Fix{cite}. Figure \ref{fig:performance} report the results of that analysis for all the distributions. With 95\% of confidence, it is possible to see that \sfl{} and \comb{}-5 have similar distributions.

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean & \textbf{580.0} (584.3)   &  \textbf{502.6} (516.4)  & \textbf{567.0} (679.7)  & \textbf{491.5} (614.0)   \\ \midrule
Median & \textbf{47.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
Shapiro &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

>>>>

In this section, we answer the research questions proposed and discuss the results obtained.
Our approach was capable of slicing a total of $260$ faults from $5$ different 
projects. The remaining faults were not considered because (1) faults
belong to the \closure{} project which requires high CPU to perform the \combpar{k} evaluation 
or (2) faults whose test outputs were not reproducible in the machine used to run the experiments.
\textbf{RQ1} reviews one of the main issues of \ds{} - missing faulty statements - whereas \textbf{RQ2}
discusses how effective is the proposed approach, \combpar{k}.

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
presents the number of faults where at least one of the faulty statements appears 
in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
classes of the projects. \combpar{k} finds the faulty statements faster than 
\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, an improvement
of $5.2\%$. $33$ of the $260$ faults do not include the faulty statements in the slicer report
after slicing.

@@

Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant. Shapiro-Wilk ~\cite{10.2307/2333709} tests the null hypothesis that results are drawn from a normal distribution. The test is perfomed for the three techniques under evaluation (\sfl{}, \comb{}-5, \comb{}-10). With 99 \% of confidence, the results tell us that the distributions are not normal. Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman~\cite{10.2307/2279372}. The null-hypothesis is that all distributions are the same. With 99 \% of confidence, the results show that the distributions are not all the same. In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis. Figure \ref{fig:performance} report the results of that analysis for all the distributions. With 95\% of confidence, it is possible to see that \sfl{} and \comb{}-5 have similar distributions.

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean & \textbf{580.0} (584.3)   &  \textbf{502.6} (516.4)  & \textbf{567.0} (679.7)  & \textbf{491.5} (614.0)   \\ \midrule
Median & \textbf{47.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}
